---
title: "Intoduction to Data"
author: "Jaime"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
```

```{r}
data(nycflights)
```

```{r}
names(nycflights)
```

```{r}
glimpse(nycflights)
```

## Analysis
### Departure Delays

```{r}
ggplot(data = nycflights, aes(x = dep_delay)) +
  geom_histogram()
```

```{r}
ggplot(data = nycflights, aes(x = dep_delay)) +
  geom_histogram(binwidth = 15)
```

```{r}
ggplot(data = nycflights, aes(x = dep_delay)) +
  geom_histogram(binwidth = 150)
```

### Exercise 1
Plot 2 seems to show the most data. Plot 3 seems to "hide" a lot of the data

### Filter by LAX
```{r}
lax_flights <- nycflights %>%
  filter(dest == "LAX")
ggplot(data = lax_flights, aes(x = dep_delay)) +
  geom_histogram()
```

### LAX summary
```{r}
lax_flights %>%
  summarise(mean_dd   = mean(dep_delay), 
            median_dd = median(dep_delay), 
            n         = n())
```

### Filter SFO in February
```{r}
sfo_feb_flights <- nycflights %>%
  filter(dest == "SFO", month == 2)
```

### Exercise 2
68

### Exercise 3
Similar to overall data. But does have outliers
```{r}
ggplot(data = sfo_feb_flights, aes(x = dep_delay)) +
  geom_histogram()
```

### Exercise 4
United Airlines with 21 delays
```{r}
sfo_feb_flights %>%
  group_by(carrier) %>%
  summarise(median_dd = median(arr_delay), iqr_dd = IQR(arr_delay), n_flights = n())
```

### Exercise 5
Outliers could cause the data to be skewed which may not be representative of the actual lowest month. 

```{r}
nycflights <- nycflights %>%
  mutate(dep_type = ifelse(dep_delay < 5, "on time", "delayed"))
```

```{r}
nycflights %>%
  group_by(origin) %>%
  summarise(ot_dep_rate = sum(dep_type == "on time") / n()) %>%
  arrange(desc(ot_dep_rate))
```

### Exercise 6
LGA 72.7% on time rate

### Exercise 7
```{r}
nycflights <- nycflights %>%
  mutate(avg_speed = distance / (air_time / 60))
```

### Exericise 8
It appears that the further the distance the faster the average speed
```{r}
ggplot(data = nycflights, aes(x = distance, y = avg_speed)) +
  geom_point()
```

### Exercise 9

```{r}
nycflights_3carriers <- nycflights %>%
  filter(carrier == "AA" | carrier == "DL" | carrier == "UA")
```

```{r}
ggplot(data = nycflights_3carriers, aes(x = dep_delay, y = arr_delay, color = carrier)) +
  geom_point()
```

