---
title: "Probability"
author: "Jaime Rodriguez"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
```

```{r}
glimpse(kobe_basket)
```

```{r}
head(kobe_basket, 9)
```

### Exercise 1
1 means one hit then a miss. 0 means there were no hits in that streak.


#### Practice

Streak counter of shots
```{r}
kobe_streak <- calc_streak(kobe_basket$shot)
```

Plotted Streak
```{r}
ggplot(data = kobe_streak, aes(x = length)) +
  geom_bar()
```

### Exercise 2
Plot above
Longest streak length was 4 made shots in a row. 
Typical streak length was 1 shot before missing. 

### Exercise 3
26 Heads
```{r}
set.seed(35797)
coin_outcomes <- c("heads", "tails")
sim_unfair_coin <- sample(coin_outcomes, size = 100, replace = TRUE,
       prob = c(0.2, 0.8))
```

```{r}
sim_unfair_coin
table(sim_unfair_coin)
```

### Exercise 4

```{r}
shot_outcomes <- c("H", "M")
sim_basket <- sample(shot_outcomes, size = 133, replace = TRUE,
                     prob = c(0.45, 0.55))
```


### Exercise 5
```{r}
sim_streak <- calc_streak(sim_basket)
```

### Exercise 6
Longest streak = 6
Typical streak = 1
```{r}
ggplot(data = sim_streak, aes(x = length)) +
  geom_bar()
```
### Exercise 7
Expected result would be somewhat similar. This is due to the shooting percentage being predetermined. If this were to change, the results would differ more.

### Exercise 8
Although the simulation has higher streaks. Kobe was able to maintain higher frequency of streaks. Compared to the simulation have more non streaks. 



















